Towards Explainability of Machine Learning Models in Insurance Pricing

### 2019-10-25 manuscript/manuscript.Rmd
add things to watch out for

In Figure \@ref(fig:fi), we show a plot of variable importances. In our particular example, we see that the "make" variable contributes most to the accuracy of the model with "sex" contributing the least. Note that these measures do not provide information regarding the directional sensitivity of the predictors on the response. This provides a way for the audience to quickly glance at the most relevant variables, and ask further question as necessary. For example, if a variable that can potentially be a proxy for a discriminatory variable appears as very important, more investigation would be warranted.

```{r fi, out.width='100%', fig.align = "center", fig.cap="Permutation feature importances for ML model.", echo = FALSE}
knitr::include_graphics("figures/fi-plot.png")
```

@@

```{r pdp, out.width='70%', fig.align = "center", fig.cap="Partial dependence plot for ML model.", echo = FALSE,  fig.env='figure*', fig.pos='h'}
knitr::include_graphics("figures/pdp-plot.png")
```

```{r breakdown, out.width='80%', fig.align = "center", fig.cap="Variable contribution plot for ML model.", echo = FALSE, fig.env = 'figure*', fig.pos = 'h'}
knitr::include_graphics("figures/breakdown-plot.png")
```

@@

@@

@@

(TODO: briefly discuss other stuff no covered)

>>>>

In Figure \@ref(fig:fi), we show a plot of variable importances. In our particular example, we see that the "make" variable contributes most to the accuracy of the model with "sex" contributing the least. This provides a way for the audience to quickly glance at the most relevant variables, and ask further question as necessary. For example, if a variable that can potentially be a proxy for a discriminatory variable appears as very important, more investigation would be warranted.

Note that these measures do not provide information regarding the directional sensitivity of the predictors on the response. Also, when there are correlated variables, one should be careful about interpretation, as the result may be biased by unrealistic records in the permuted dataset. Another ramification of a group correlated variables is that their inclusion may cause each to appear less important than if only one is included in the model.

```{r fi, out.width='100%', fig.align = "center", fig.cap="Permutation feature importances for the neural network model.", echo = FALSE}
knitr::include_graphics("figures/fi-plot.png")
```

@@

```{r pdp, out.width='70%', fig.align = "center", fig.cap="Partial dependence plot for the neural network model.", echo = FALSE,  fig.env='figure*', fig.pos='h'}
knitr::include_graphics("figures/pdp-plot.png")
```

```{r breakdown, out.width='80%', fig.align = "center", fig.cap="Variable contribution plot for the neural network model.", echo = FALSE, fig.env = 'figure*', fig.pos = 'h'}
knitr::include_graphics("figures/breakdown-plot.png")
```

@@

As with permutation feature importance, one should be careful when interpreting PDP when there are strongly correlated variables. Since we average over the marginal distribution of the rest of the variables, we may take into account unrealistic data (e.g. high vehicle age for a model that is brand new).

@@

As noted earlier, the ordering of variables has an impact on the contributions calculated, especially for models that are non-additive, which could cause inconsistent explanations. There are several approaches to ameliorate this phenomenon, including selecting variables with the largest contributions first, including interactions terms, and averaging over possible orderings; these are discussed further in @biecekPMVEE and its references.

@@

(TODO: briefly discuss other stuff not covered)
